Validated Model Counting Data \\ Version of \today

### 2023-02-28 doc/mc-data.tex
Small updates

\begin{figure}
\centering{%
\begin{tikzpicture}[scale = 1.00]
  \begin{axis}[mark options={scale=0.55},grid=both, grid style={black!10}, ymode=log, ymin=100, ymax=10000000000,
      legend style={at={(0.30,0.98)}},
      legend cell align={left},
                              x post scale=2.0, y post scale=2.0,
                              xmode=log, xmin=001,xmax=10000,
                              xtick={0.01, 0.1,1.0,10,100,1000,10000}, xticklabels={0.01, 0.1, 1.0, 10, 100, {1,000}, {10,000}},
                              ytick={100,1000, 10000, 100000, 1000000, 10000000, 100000000, 1000000000, 1e10}, yticklabels={$10^2$,$10^3$,$10^4$,$10^5$,$10^6$,$10^7$,$10^8$,$10^9$,$10^{10}$},
                              xlabel={D4 runtime (seconds)}, ylabel={Defining Clauses},
%                              title={D4 Defining Clause Generation}
            ]
    \input{data-formatted/time+defining-failure}
    \input{data-formatted/time+defining-success}
    \legend{
      \scriptsize \textsf{Limit exceeded},
      \scriptsize \textsf{Validated},
    }
 \end{axis}
\end{tikzpicture}
} % centering
\caption{Number of defining clauses in generated POG as function of D4 runtime}
\label{fig:generate:d4:log}
\end{figure}

@@

\begin{figure}
\centering{%
\begin{tikzpicture}[scale = 1.00]
  \begin{axis}[mark options={scale=0.55},grid=both, grid style={black!10}, ymode=log, ymin=0.01, ymax=100000,
                              x post scale=2.0, y post scale=2.2,
                              xmode=log,xmin=0.01,xmax=10000,
                              xtick={0.01, 0.1,1.0,10,100,1000,10000}, xticklabels={0.01, 0.1, 1.0, 10, 100, {1,000}, {10,000}},
                              ytick={0.01, 0.1,1.0,10,100,1000,10000,100000}, yticklabels={0.01, 0.1, 1.0, 10, 100, {1,000},{10,000},{100,000}},
                              xlabel={D4 runtime (seconds)}, ylabel={CRAT generation and checking runtime (seconds)},
%                              title={D4 Defining Clause Generation}
            ]
    \addplot[mark=none, color=lightblue] coordinates{(0.01,0.01) (10000.0,10000.0)};
    \addplot[mark=none, color=lightblue] coordinates{(0.01,0.1) (10000,100000)};
    \addplot[mark=none, color=lightblue] coordinates{(0.01,1.0) (1000,100000)};
    \addplot[mark=none, color=lightblue] coordinates{(0.01,10.0) (1000,1000000)};
    \input{data-formatted/time-d4-verify}
    \node[left] at (axis cs: 0.09,0.12) {$1\times$};
    \node[left] at (axis cs: 0.09,1.2) {$10\times$};
    \node[left] at (axis cs: 0.09,12.0) {$100\times$};
    \node[left] at (axis cs: 0.09,120.0) {$1000\times$};

@@

Here are other ways to summarize the impact on proof length:
\begin{itemize}
\item None of the 80 benchmarks require more than $10^7$
proof clauses when both optimizations are used.  Without lemmas, 19
rise above that threshold.  Without literal merging, 7 due.  Without
either, 25 rise above the threshold.  Two of the benchmarks require
more than $10^8$ proof clauses without lemmas.
\item Of the 80 benchmark problems evaluated, and comparing with both
  optimizations disabled, 55 had the number of proof clauses reduced
  by at least 10\% by using lemmas, 19 by using literal merging, and
  69 by enabling both optimizations.
\end{itemize}

@@

Here is another way to summarize the impact on the combined time to generate and validate the CRAT file:
\begin{itemize}
\item Of the 80 benchmark problems evaluated, and comparing with both
  optimizations disabled, 50 had the time reduced by at least 10\% by
  using lemmas, 27 by using literal merging, and 63 by enabling both
  optimizations.
\end{itemize}

>>>>

\begin{figure}
\centering{%
\begin{tikzpicture}[scale = 1.00]
  \begin{axis}[mark options={scale=0.55},grid=both, grid style={black!10}, ymode=log, ymin=100, ymax=3000000000,
      legend style={at={(0.30,0.98)}},
      legend cell align={left},
                              x post scale=2.0, y post scale=2.0,
                              xmode=log, xmin=001,xmax=4000,
                              xtick={0.01, 0.1,1.0,10,100,1000,10000}, xticklabels={0.01, 0.1, 1.0, 10, 100, {1,000}, {10,000}},
                              ytick={100,1000, 10000, 100000, 1000000, 10000000, 100000000, 1000000000, 1e10}, yticklabels={$10^2$,$10^3$,$10^4$,$10^5$,$10^6$,$10^7$,$10^8$,$10^9$,$10^{10}$},
                              xlabel={D4 runtime (seconds)}, ylabel={Defining Clauses},
%                              title={D4 Defining Clause Generation}
            ]
    \input{data-formatted/time+defining-failure}
    \input{data-formatted/time+defining-success}
    \legend{
      \scriptsize \textsf{Limit exceeded},
      \scriptsize \textsf{Validated},
    }
 \end{axis}
\end{tikzpicture}
} % centering
\caption{Number of defining clauses in generated POG as function of D4 runtime}
\label{fig:generate:d4:log}
\end{figure}

@@

\begin{figure}
\centering{%
\begin{tikzpicture}[scale = 1.00]
  \begin{axis}[mark options={scale=0.55},grid=both, grid style={black!10}, ymode=log, ymin=0.01, ymax=20000,
                              x post scale=2.0, y post scale=2.2,
                              xmode=log,xmin=0.01,xmax=4000,
                              xtick={0.01, 0.1,1.0,10,100,1000,10000}, xticklabels={0.01, 0.1, 1.0, 10, 100, {1,000}, {10,000}},
                              ytick={0.01, 0.1,1.0,10,100,1000,10000,100000}, yticklabels={0.01, 0.1, 1.0, 10, 100, {1,000},{10,000},{100,000}},
                              xlabel={D4 runtime (seconds)}, ylabel={CRAT generation and checking runtime (seconds)},
%                              title={D4 Defining Clause Generation}
            ]
    \addplot[mark=none, color=lightblue] coordinates{(0.1,0.01) (10000.0,1000.0)};
    \addplot[mark=none, color=lightblue] coordinates{(0.01,0.01) (10000.0,10000.0)};
    \addplot[mark=none, color=lightblue] coordinates{(0.01,0.1) (10000,100000)};
    \addplot[mark=none, color=lightblue] coordinates{(0.01,1.0) (1000,100000)};
    \addplot[mark=none, color=lightblue] coordinates{(0.01,10.0) (1000,1000000)};
    \input{data-formatted/time-d4-verify}
    \node[left] at (axis cs: 0.9,0.12) {$0{.}1\times$};
    \node[left] at (axis cs: 0.09,0.12) {$1\times$};
    \node[left] at (axis cs: 0.09,1.2) {$10\times$};
    \node[left] at (axis cs: 0.09,12.0) {$100\times$};
    \node[left] at (axis cs: 0.09,120.0) {$1000\times$};

@@

Here are other ways to summarize the impact on proof length:
\begin{itemize}
\item None of the 80 benchmarks require more than $10^7$
proof clauses when both optimizations are used.  Without lemmas, 19
rise above that threshold.  Without literal merging, 7 due.  Without
either, 25 rise above the threshold.  Two of the benchmarks require
more than $10^8$ proof clauses without lemmas.
\item
  Of the 80 benchmark problems evaluated, and comparing with both
  optimizations disabled, 47 had the number of proof clauses reduced
  by a factor of 2 by using lemmas, 14 by using literal merging, and
  60 by enabling both optimizations.
\end{itemize}

@@

Here is another way to summarize the impact on the combined time to generate and validate the CRAT file:
\begin{itemize}
\item Of the 80 benchmark problems evaluated, and comparing with both
  optimizations disabled, 40 had the time reduced by at least a factor of 2
  using lemmas, 7 by using literal merging, and 49 by enabling both
  optimizations.
\end{itemize}
